Constructing the transition graphs of interacting hysterons

### 2022-07-01 Paper_draft.tex
Added reference to Mungan & Terzi (2020) for ordering of switching fields

Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields. The ordering for each graph can be easily identified by considering the main loop: that is, the sequence of down transitions connecting the state with all $s_i = 1$ to that with all $s_i=0$. We accordingly use the main loop as an identifier for the Preisach graphs. For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1).\\ 

>>>>

Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields\cite{terzimungan2020}. The ordering for each graph can be easily identified by considering the main loop: that is, the sequence of down transitions connecting the state with all $s_i = 1$ to that with all $s_i=0$. We accordingly use the main loop as an identifier for the Preisach graphs. For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1) \cite{terzimungan2020}.\\ 
